%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	  \textbf{\Huge Youssef El Gharably} & \\
	  701 Harrisburg Ave, Lancaster, PA, 17603, USA & \\
	  \href{tel:+12232789055}{+1 (223) 278-9055} & \href{mailto:yelghara@fandm.edu}{yelghara@fandm.edu}\\
	  \href{https://github.com/yelgharably}{GitHub: yelgharably} & \href{mailto:youssefelgharably0404@gmail.com}{youssefelgharably0404@gmail.com}\\
	\end{tabular*}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Franklin and Marshall College}{August 2022 -- May 2025}
      {Major in Astrophysics with a Minor in Applied Mathematics, 3.80 GPA}
      {Lancaster, PA}
      
      {\textit{Honors' and Dean's List | Charles A. Dana Scholar}}
      
    \resumeSubheading
      {Washington University in St. Louis}{December 2023 -- January 2024}
      {Visiting student in Mckelvey School of Engineering for J-Term, 4.00 GPA}
      {St. Louis, MO}

      {\textit{Student of J-Term 2024 taking MEMS253}}
     
     \resumeSubheading
       {Gharbiya STEM High School}{September 2019 -- July 2022}
       {Mathematics Division, 3.82 GPA}
       {Tanta, Egypt}
       
       {\textit{Ranked 82/2500 students in the country.}}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-1pt, parsep=3pt]
                \item PHY112 - Intro to Electromagnetism (Fa22)
                 \item Mathworks - MatLab Fundamentals (W22)
                \item AST121 - Intro to Astrophysics (Sp23)
                \item PHY223 - Modern Physics (Fa23)
                \item MAT229 - Linear Algebra and Differential Equations (Fa23)
                \item MEMS253 - Statics and Mechanics of Materials (Winter 23, WashU.)
                \item PHY226 - Classical Mechanics (Sp24)
                \item AST322 - Stellar Astrophysics (Sp24)
                \item MAT215 - Statisitcal Modeling (Su24)
                \item PHY331 - Mathematical Methods of Physics (Fa24)
                \item PHY322 - Experimental Physics: Electronics (Fa24)
                \item PHY333 - Electromagnetism (Fa24)
                \item MAT216 - Probability and Statistics (Fa24)
                \item PHY344 - Quantum Mechanics (Planned, S25)
                \item MAT372 - Origami Math (Planned, S25)
                \item AST332 - Galaxies and Cosmology (Planned, S25)
                \item AST422 - Advanced Methods in Astrophysics (Planned)
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Physics and Astronomy Department, Franklin and Marshall College}{August 2023 -- December 2023}
      {Research Assistant (AST290, Fall 23), Fronefield Crawford Ph.D.}{Lancaster, PA}
      \resumeItemListStart
      \resumeItem{Project Title: Investigation and Development of the Small Radio Telescope in Franklin and Marshall Campus.}
    \resumeItem{Developed a comprehensive plan for the investigation of the Small Radio Telescope owned by the Physics Department.}
    \resumeItem{Implemented scripts on the control computer to acquire radio data, optimizing the telescope's performance and calibration.}
    \resumeItem{Enhanced the quality of Astronomical observation labs conducted by astrophysics professors in classes.}
    \resumeItem{Investigated the mechanics and electronic systems of Radio Telescopes with the Department's electronics engineer to deepen knowledge of Astronomical Instruments and telescopes.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Physics and Astronomy Department, Franklin and Marshall College}{June 2024 -- July 2024}
      {Summer Hackman Scholar Research Assistant, Ryan Trainor Ph.D.}{Lancaster, PA}
      \resumeItemListStart
       \resumeItem{Project Title: Characterizing Black Holes and the Circumgalactic Medium with Keck Cosmic Web Imager}
       \resumeItem{Developed Monte Carlo Markov Chain algorithim using python for creating statistical models of the Mariposa nebula.}
       \resumeItem{Derived substantial results from models to characterize AGN's through spectroscopy readings.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Physics and Astronomy Department, Franklin and Marshall College}{Jan 2024 -- August 2024}
      {Research Assistant (AST390, Spring 2024) and Summer Hackman Scholar, Deborah Schmidt Ph.D.}{Lancaster, PA}
      \resumeItemListStart
      \resumeItem{Project Title: Investigations of Chemical Complexity in Proto-Planetary Nebulae, currently through the process of writing a paper to publish.}
       \resumeItem{Co-authored proposals for observations in the Arizona Radio Observatory.}
       \resumeItem{Wrote a script to automatically produce publication worthy figures based on any CLASS data during Summer 2024. Published script on GitHub for other astronomers to benefit from it.}
\resumeItem{Utilized GILDAS tools to determine optimal observation times.}
\resumeItem{Analyzed radio data from Arizona Radio Observatory to identify HCO, HCN, HNC, and HCO3N compounds in protoplanetary nebulae.}
\resumeItem{Played a key role in the first-ever detection of HCO3N molecules in a protoplanetary nebula through data analysis.}

      \resumeItemListEnd
      
    \resumeSubheading
      {Earth and Environment Department, Franklin and Marshall College}{Jan 2024 -- May 2024}
      {Research Assistant in Landmine Detection Research (PHY390, Spring 24), Fronefield Crawford Ph.D.}{Lancaster, PA}
      \resumeItemListStart
        \resumeItem{Tested optical systems to detect tripwires using Python and Raspberry Pi.}
\resumeItem{Assisted in construction of the mechanical arm that integrates the optical system.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Physics and Astronomy Department, Franklin and Marshall College}{Jan 2023 -- May 2023}
      {Research Assistant in NANOGRAV Pulsar Survey (AST290, Spring 23), Fronefield Crawford Ph.D.}{Lancaster, PA}
      \resumeItemListStart
        \resumeItem{Assisted the Physics Department in Franklin and Marshall College with their research on surveying potential Pulsar star signals brought by observations of the Parkes Telescope in Australia.}
      \resumeItemListEnd
     
\resumeSubHeadingListEnd

\vspace{-16pt}

\section{Teaching Experience}
\resumeSubHeadingListStart

	 \resumeSubheading
	    {Governor’s STEM Institute Camp at Green Bank Observatory}{July 2023}
	    {Mentor at GSI}{Green Bank, WV}
	    \resumeItemListStart
	      \resumeItem{Selected alongside 10 other undergraduate mentors to advise and lead an astronomy project to determine the efficiency of the 40-foot-telescope for rising 9th graders from West Virginia}
	      \resumeItem{WVGSI is a program funded by West Virginia’s Governor and hosted at Green Bank Observatory to educate K-12 students about radio astronomy with hands-on experience.}
	      \resumeItem{Residential Adviser for bunkhouse during the program for the 9th graders.}
	    \resumeItemListEnd
  
	  \resumeSubheading
	      {Quantitative and Science Center, Franklin and Marshall College}{August 2023 -- Present}{Mathematics Tutor for Q\&SC for Calculus 1, 2, 3 and Linear Algebra, Differential Equations}{Lancaster, PA}
	      \resumeItemListStart
	        \resumeItem{Worked in coordination with the Math department to tutor students in math classes on campus via individual appointments and Drop In tutoring.}
	        \resumeItem{Assigned to multiple math sections to be the main tutor, professors reported that students who came to my tutoring sessions had a significant increase in their grades for calculus.}
	        \resumeItem{Significantly improved my tutees' math grades.}
	      \resumeItemListEnd
	      
	      \resumeSubheading
      {Physics and Astronomy Department, Franklin and Marshall College}{Jan 2024 -- May 2024}
      {Lab Teaching Assistant for AST121 (Introduction to Astrophysics)}{Lancaster, PA}
      \resumeItemListStart
        \resumeItem{Assisted in the introduction to astrophysics lab, helped a class of 25 students navigate radio astronomy and basic astrophysics concepts.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-16pt}

\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Sparklab in Franklin and Marshall}{August 2022 - May 2023, January 2024}
    {Tech Tutor}{Lancaster, PA}
    \resumeItemListStart
      \resumeItem{Assisted students on campus with their technical issues, operating poster printers, 3d printers, resin printers, and managing classroom technical equipment.}
      \resumeItem{Constructed multiple projects using soldiering, Arduino, and Rasberry Pi.}
      \resumeItem{Repaired and maintained Ultimaker and Prusa 3D Printers.}
      \resumeItem{Maintained and maintained electronics and hardware.}
    \resumeItemListEnd


    \resumeSubheading
    {Shadeck-Fackenthal Library in Franklin and Marshall}{August 2022 - May 2023}
    {Circulation Assistant}{Lancaster, PA}
    \resumeItemListStart
      \resumeItem{Assisted students and patrons in retrieving books and browsing in the College Library}
      \resumeItem{Shelved returned books once or twice weekly throughout the library.}
    \resumeItemListEnd


\resumeSubHeadingListEnd

\vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
    	{\textbf{Automated publishing-worthy figure builder for radio observations.} $|$ \emph{Python}}{Summer 2024}
    	\vspace{-25pt}
    
    \resumeProjectHeading
    	{\textbf{Monte Carlo Markov Chain Statistical Modeling Program for Active Galaxy Nucleai} $|$ \emph{Python}}{Summer 2024}
    	\vspace{-25pt}
    \resumeProjectHeading
    	{\textbf{Finite Element Analysis Material Bending simulator} $|$ \emph{Python}} {Spring 2024}
    	\vspace{-25pt}
    
      \resumeProjectHeading
          {\textbf{LED Panel For SparkLab at Franklin and Marshall College} $|$ \emph{Micro-controller programming}}{January 2023}
          \vspace{-25pt}
      \resumeProjectHeading
          {\textbf{Solar Tracker Thermal Generator for High School Capstone} $|$ \emph{Arduino}}{September 2021 - January 2022}
          \resumeItemListStart
            \resumeItem{Designed a system using optics to track and focus the sun's thermal energy into a steam engine}
          \resumeItemListEnd 
          \vspace{-3pt}
    \resumeSubHeadingListEnd
\vspace{-7.5pt}

%-----------Presentations-------
\section{Oral Presentations}
\resumeSubHeadingListStart

\resumeSubheading
	{Modeling Spectral Emissions for characterizing real data}{July 2024}
	{Summer Hackman Research Scholar, Professor Ryan Trainor}{Lancaster, PA}
	\resumeItemListStart
		\resumeItem{Presented my work on Monte Carlo Markov Chain modeling of spectral emissions using Cloudy data aganist CECILIA data.}
		\resumeItem{No formal paper is wrriten yet, research summary could be found \href{https://drive.google.com/file/d/1pdic1Xo9b_9rP_IwuPj-X7j9XGsKKe-2/view?usp=sharing}{\textit{here.}}}
	\resumeItemListEnd

\resumeSubheading
    {The Theories behind the Maximum Size of White Dwarfs}{April 2024}
    {Stellar Astrophysics (AST322), Professor Deborah Schmidt}{Lancaster, PA}
    \resumeItemListStart
      \resumeItem{Presented the work of S. Chandrasekhar published by the Indian Academy of Sciences for a class project}
    \resumeItemListEnd

\resumeSubheading
	{CHIME Telescopes and the International Pulsar Timing Array}{May 2024}
	{Stellar Astrophysics (AST322), Professor Deborah Schmidt}{Lancaster, PA}
	\resumeItemListStart
		\resumeItem{Presented my final paper of Stellar Astrophysics as an investigation of an ongoing area of research in Stellar Astrophysics}
		\resumeItem{The paper could be accessed \href{https://drive.google.com/file/d/1cJZISS8DrxotopiGoOAdU125DQ4NQAvo/view?usp=sharing}{\textit{here}}, written in the ApJ format.}
	\resumeItemListEnd

\resumeSubheading
	{Finite Element Analysis using Python to simulate material bending}{May, 2024}
	{Classical Mechanics (PHY226), Professor Ryan Trainor}{Lancaster, PA}
	\resumeItemListStart
		\resumeItem{Presenting my final project for the computational physics lab of Classical Mechanics class.}
		\resumeItem{The project report could be accessed \href{https://drive.google.com/file/d/1223KLIkQvRVcOTqhtgjDWnJgVCJZH9Ih/view?usp=sharing}{\textit{here}}.}
	\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-12pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, Arduino, Wolfram Mathematica, MatLab, LaTeX, R, Rmarkdown.} \\
      \textbf{Hardware Experience}{: Robotics, 3D Printers, Windows PC Hardware, Soldiering.} \\
      \textbf{Design Software and Other Skills}{: 3D Printing, Blender, Photoshop, Lightroom, Premiere} \\
     \textbf{Languages}{: Arabic(Native/Bilingual Proficiency) - English (Native/Bilingual Proficiency) - French (Limited Working Proficiency)}\\
     \textbf{Hobbies}{: Photography, Programming, Reading.} \\
     \textbf{Currently Learning}{: CAD, Finite Element Analysis, Mechanical Systems.} \\
    }}
 \end{itemize}


 %-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Muslim Student Association}{August 2023 -- May 2024}{President}{Franklin and Marshall College}
            \resumeItemListStart
                \resumeItem{Rewrote the Muslim Student Associations' constitution and added addendums to ensure inclusion and condem hate speech aganist all religions.}
                \resumeItem{Represent the Muslim student body in the Student Union Congress, ensure accommodation for the Muslim student body on campus, and participate in philanthropy for underrepresented Muslim countries and regions.}
                \resumeItem{Significantly contributed in initiatives and meeting with the college administration and other organizations on campus to counteract hate speech, Islamophobia, and anti-semitism.}
                \resumeItem{Planned and led the preparations for Ramadan in both spring 2023, and spring 2024; had meetings with the campus dining services and organized surveys with office of faith and meaning, and Diversity, Equity, Inclusion office to accommodate Muslim students' needs for Ramadan.}
            \resumeItemListEnd

        \resumeSubheading{Facilitator and Student Panelist for Identity, Power, and Inequality class.}{Fall 2023}{Panelist and Student Leader}{Franklin and Marshall College}
            \resumeItemListStart
                \resumeItem{Invited as a guest panelist for a student panel in INT127 (Identity, Power, and Inequality) due to known efforts on campus to establish peace in the student body and advocacy for minorities.}
            \resumeItemListEnd

        \resumeSubheading{Competitive College Club, EducationUSA}{February 2020 - May 2023}{Current Alumni, Former Vice President}{Amideast Alexandria, Egypt}
            \resumeItemListStart
                \resumeItem{The Education USA Competitive College Club (CCC) is an intensive group advising program that assists top high school students who want to be competitive applicants to U.S. colleges and universities.}
                \resumeItem{Participated in the intensive mentorship program, standardized tests club, creative writing club, 2-week intensive boot camp with intensive tasks and book club in which I received guidance from graduating seniors and alumni.}
                \resumeItem{Chosen as Vice President by Amideast Advisers as of February 2021.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd
\end{document}
